Psychological Needs During Intergroup Contact: Three Experience Sampling Studies

### 2022-10-29 Methods-and-Results.Rmd
shaded fix
table format

mdlTblGeneralLong %>%
    replace(is.na(.), "") %>%
  kbl(
    .,
    caption = "Intergroup General",
    format = "latex",
    linesep = "",
    booktabs = TRUE,
    col.names = c("", rep(c("$B$", "$\\beta$"), (ncol(.)-1)/2)),
    align = c("l", rep("c", ncol(.) - 1)),
    escape = FALSE,
    digits = 3
  )  %>%
  kable_classic() %>%
  add_header_above(
    .,
    c(
      "",
      "Study 1" = 2,
      "Study 2" = 2,
      "Study 3" = 2
    )
  ) %>%
  pack_rows("Between Participant [aggregated linear regression] (Effect Size = $\\eta_{partial}$)", 1, 6, escape = FALSE) %>%
  # pack_rows("Within Participants [multilevel linear regression] (Effect Size = $\\beta$)", 6, 9, escape = FALSE) %>%
  kableExtra::footnote(
    .,
    general = c("**** $p$ < .0001, *** $p$ < .001, ** $p$ < .01, * $p$ < .05"), 
    escape = FALSE
  ) %>%
  kable_styling(latex_options = "scale_down") %>%
  gsub("\\begin{table}", "\\begin{table}\n\\begin{minipage}[t][\\textheight][t]{\\textwidth}", ., fixed = TRUE) %>% # fix table position
  gsub("\\end{table}", "\\end{minipage}\n\\end{table}", ., fixed = TRUE) %>% # fix table position
  kableExtra::landscape() %>%
  save_kable("Tables/mdlContactGeneralLong.tex")
```

@@

```{r Export Path Models}
save(shortMdlPath, 
     file = "data/theoryMdlTabl.RData")
```

>>>>

mdlTblGeneralLong %>%
  replace(is.na(.), "") %>%
  mutate(
    B = ifelse(
      B.1 == "", paste("\\multicolumn{6}{c}{", B, sep=""),
      B
    )
  ) %>%
  kbl(
    .,
    caption = "Intergroup General",
    format = "latex",
    linesep = "",
    booktabs = TRUE,
    col.names = c("", rep(c("$B$", "$\\beta$"), (ncol(.)-1)/2)),
    align = c("l", rep("c", ncol(.) - 1)),
    escape = FALSE,
    digits = 3
  )  %>%
  kable_classic() %>%
  add_header_above(
    .,
    c(
      "",
      "Study 1" = 2,
      "Study 2" = 2,
      "Study 3" = 2
    )
  ) %>%
  pack_rows("Within Participants [multilevel linear regression] (Effect Size = $\\beta$)", 1, 6, escape = FALSE) %>%
  pack_rows("Between Participant [aggregated linear regression] (Effect Size = $\\eta_{partial}$)", 7, nrow(mdlTblGeneralLong), escape = FALSE) %>%
  kableExtra::footnote(
    .,
    general = c("**** $p$ < .0001, *** $p$ < .001, ** $p$ < .01, * $p$ < .05"), 
    escape = FALSE
  ) %>%
  kable_styling(latex_options = "scale_down") %>%
  gsub("\\begin{table}", "\\begin{table}\n\\begin{minipage}[t][\\textheight][t]{\\textwidth}", ., fixed = TRUE) %>% # fix table position
  gsub("\\end{table}", "\\end{minipage}\n\\end{table}", ., fixed = TRUE) %>% # fix table position
  gsub(" &  &  &  &  & \\", "}\\", ., fixed = TRUE) %>% # fix table position
  kableExtra::landscape() %>%
  save_kable("Tables/mdlContactGeneralLong.tex")
```

@@

```{r Export Path Models, include=FALSE}
save(shortMdlPath, 
     file = "data/theoryMdlTabl.RData")
```
